### 2015-09-14 vmcai-2016-tex/abstract.tex
edits to the abstract

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state. A fundamental problem
with using these guarded value sets is the creation of test inputs for
programs accepting symbolic reference input parameters. Although
several solutions have been proposed, none have been proven to be
sound and complete with respect to the properties provable by
generalized symbolic execution (GSE). This work presents a method for
initializing reference inputs in a symbolic input heap using guarded
value sets that exactly preserves GSE semantics. A correctness proof
for the initialization scheme is provided, as well as the results of
an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
initialization technique can be used to ensure that guarded value set
based symbolic execution engines operate in a provably correct manner
with regards to symbolic references.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE) given certain user-defined
bounds. This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided, as well as the results of an empirical evaluation
of a proof-of-concept implementation showing a real increase in the
size and number of analyzed heaps compared to existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.
